\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

% Section formatting
\titleformat{\section}
  {\normalfont\Large\bfseries}
  {}{0em}{}[\vspace{-0.5em}\rule{\textwidth}{0.4pt}]

\pagestyle{empty}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\LARGE \textbf{Dr. Robert Johnson}} \\
    \vspace{0.1cm}
    Department of Computer Science, Stanford University \\
    Email: robert.johnson@stanford.edu | Phone: (555) 123-4567 \\
    Website: \href{https://robertjohnson.edu}{robertjohnson.edu} | 
    Google Scholar: \href{https://scholar.google.com/citations?user=xxx}{Profile}
\end{center}

\vspace{0.3cm}

% ===== RESEARCH INTERESTS =====
\section*{Research Interests}
Machine Learning, Natural Language Processing, Computer Vision, Deep Learning, Artificial Intelligence, Human-Computer Interaction

\vspace{0.2cm}

% ===== EDUCATION =====
\section*{Education}

\textbf{Ph.D. in Computer Science} \hfill \textit{2018 - 2023} \\
Massachusetts Institute of Technology (MIT), Cambridge, MA \\
Dissertation: \textit{``Advanced Neural Architectures for Natural Language Understanding''} \\
Advisor: Prof. Jane Smith | GPA: 4.0/4.0

\vspace{0.15cm}

\textbf{M.S. in Computer Science} \hfill \textit{2016 - 2018} \\
Stanford University, Stanford, CA \\
Thesis: \textit{``Deep Learning Approaches to Sentiment Analysis''} \\
GPA: 3.95/4.0

\vspace{0.15cm}

\textbf{B.S. in Computer Science} \hfill \textit{2012 - 2016} \\
University of California, Berkeley, CA \\
\textit{Summa Cum Laude} | GPA: 3.98/4.0

\vspace{0.2cm}

% ===== ACADEMIC POSITIONS =====
\section*{Academic Positions}

\textbf{Assistant Professor} \hfill \textit{2023 - Present} \\
Department of Computer Science, Stanford University, Stanford, CA
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Teaching graduate and undergraduate courses in Machine Learning and NLP
    \item Leading research group of 8 Ph.D. students and 4 postdoctoral researchers
    \item Secured \$2M in research funding from NSF and industry partners
\end{itemize}

\vspace{0.15cm}

\textbf{Postdoctoral Researcher} \hfill \textit{2023} \\
Computer Science and Artificial Intelligence Laboratory (CSAIL), MIT, Cambridge, MA
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Conducted research on large language models and their applications
    \item Collaborated with industry partners on AI safety and alignment
\end{itemize}

\vspace{0.2cm}

% ===== PUBLICATIONS =====
\section*{Selected Publications}

\textbf{Journal Articles}

\begin{enumerate}[leftmargin=*, itemsep=4pt]
    \item \textbf{Johnson, R.}, Smith, J., \& Brown, A. (2024). ``Efficient Transformers for Long-Context Understanding.'' \textit{Nature Machine Intelligence}, 6(2), 123-145. [Impact Factor: 25.8]
    
    \item \textbf{Johnson, R.}, Lee, K., \& Chen, M. (2023). ``Neural Architecture Search for Natural Language Processing.'' \textit{Journal of Machine Learning Research}, 24(1), 1-42.
    
    \item Smith, J., \textbf{Johnson, R.}, \& Davis, P. (2023). ``Multimodal Learning with Vision and Language Models.'' \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence}, 45(8), 3456-3478. [Impact Factor: 24.3]
\end{enumerate}

\vspace{0.15cm}

\textbf{Conference Papers}

\begin{enumerate}[leftmargin=*, itemsep=4pt]
    \item \textbf{Johnson, R.}, et al. (2024). ``Scaling Laws for Large Language Models.'' \textit{Proceedings of NeurIPS 2024}. (Oral Presentation, Acceptance Rate: 0.5\%)
    
    \item \textbf{Johnson, R.}, \& Smith, J. (2023). ``Few-Shot Learning with Prompt Engineering.'' \textit{Proceedings of ACL 2023}, pp. 1234-1245. (Best Paper Award)
    
    \item Chen, M., \textbf{Johnson, R.}, et al. (2023). ``Attention Mechanisms in Vision Transformers.'' \textit{Proceedings of CVPR 2023}, pp. 5678-5690.
    
    \item \textbf{Johnson, R.}, Brown, A., \& Lee, K. (2022). ``Transfer Learning for Low-Resource Languages.'' \textit{Proceedings of EMNLP 2022}, pp. 3456-3467.
\end{enumerate}

\vspace{0.2cm}

% ===== GRANTS & FUNDING =====
\section*{Grants \& Funding}

\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item \textbf{NSF CAREER Award} (\$500,000) \hfill \textit{2024 - 2029} \\
    ``Foundations of Efficient and Interpretable Neural Language Models''
    
    \item \textbf{Google Research Award} (\$150,000) \hfill \textit{2024} \\
    ``Multimodal AI for Accessibility Applications''
    
    \item \textbf{Amazon Research Award} (\$100,000) \hfill \textit{2023} \\
    ``Large Language Models for Code Generation''
    
    \item \textbf{NSF Graduate Research Fellowship} (\$138,000) \hfill \textit{2018 - 2021}
\end{itemize}

\vspace{0.2cm}

% ===== TEACHING EXPERIENCE =====
\section*{Teaching Experience}

\textbf{Stanford University}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item CS 229: Machine Learning (Graduate) \hfill \textit{Fall 2023, Fall 2024}
    \item CS 224N: Natural Language Processing with Deep Learning \hfill \textit{Spring 2024}
    \item CS 221: Artificial Intelligence: Principles and Techniques \hfill \textit{Winter 2024}
\end{itemize}

\vspace{0.15cm}

\textbf{MIT}
\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item 6.036: Introduction to Machine Learning (Teaching Assistant) \hfill \textit{2019 - 2022}
    \item 6.864: Advanced Natural Language Processing (Guest Lecturer) \hfill \textit{2022}
\end{itemize}

\vspace{0.2cm}

% ===== HONORS & AWARDS =====
\section*{Honors \& Awards}

\begin{itemize}[leftmargin=*, itemsep=2pt]
    \item ACL Best Paper Award \hfill \textit{2023}
    \item MIT Presidential Fellowship \hfill \textit{2018}
    \item NSF Graduate Research Fellowship \hfill \textit{2018}
    \item Berkeley EECS Distinguished Graduate Award \hfill \textit{2016}
    \item Phi Beta Kappa Honor Society \hfill \textit{2016}
\end{itemize}

\vspace{0.2cm}

% ===== PROFESSIONAL SERVICE =====
\section*{Professional Service}

\textbf{Conference Reviewing:} NeurIPS, ICML, ICLR, ACL, EMNLP, CVPR, ICCV \\
\textbf{Journal Reviewing:} JMLR, TACL, IEEE TPAMI \\
\textbf{Program Committee:} ACL 2024 (Area Chair), EMNLP 2024 (Senior PC) \\
\textbf{Workshop Organization:} Co-organizer, Workshop on Efficient NLP at EMNLP 2024

\vspace{0.2cm}

% ===== TECHNICAL SKILLS =====
\section*{Technical Skills}

\textbf{Programming:} Python, C++, Java, R, MATLAB \\
\textbf{ML Frameworks:} PyTorch, TensorFlow, JAX, Hugging Face Transformers \\
\textbf{Tools:} Git, Docker, Kubernetes, AWS, Google Cloud Platform \\
\textbf{Languages:} English (Native), Spanish (Fluent), Mandarin (Intermediate)

\end{document}

