Ashutosh Kumar Tejaswi
§ GithubUnknown | ï Linkedin | # Ash@gmail.com | H +917251455525
Summary
Full Stack Developer skilled in building end-to-end web applications with expertise in JavaScript (React,
Next.js), Python (Django, Flask), and scalable backend architectures. Experienced in designing RESTful
APIs, integrating databases (MongoDB, MySQL, PostgreSQL), and deploying production-ready solutions
on cloud platforms. Proficient in creating responsive frontends with React/Tailwind and optimizing
backends for real-time performance. Strong foundation in AI/ML integration, data-driven applications,
and interactive dashboards, bridging software engineering with intelligent system design. Collaborative
team player with hands-on project experience and proven ability to translate business needs into robust,
user-friendly applications.
Projects
Rooftop Solar Energy Generation Prediction Code Link
• Developed a lightweight, scalable machine learning model for hourly rooftop solar output, showcasing
proficiency in data exploration, preprocessing, and model development.
• Outperformed deep learning baselines with an optimized model, achieving RMSE = 0.0391 and R²
= 0.9617.
• Demonstrated proficiency in prototyping and testing by optimizing the model for deployment with a
low average inference time (6 ms), enabling real-time integration.
• Documented development process and methodologies by authoring an IEEE-format research paper
draft, comparing multiple models (CatBoost, LSTM, Bi-LSTM, GRU, Transformer).
Smriti AI – Instant Chatbot Generator Code Link
• Built a platform to generate fully customized, low-code chatbots in under a minute, leveraging Gen-
erative AI frameworks for company- and product-aware conversations.
• Enabled direct export of the chatbot as an iframe script, allowing users to embed a visually appealing,
ready-to-deploy assistant on any website with minimal effort.
• Applied advanced Natural Language Processing (NLP) for multi-format data ingestion (text,
PDF), ensuring accurate knowledge transfer and high-quality model training.
• Engineered a robust backend for efficient data parsing, cutting setup time by over 90% and making
deployment accessible to non-technical users.
RTVNR & Location Tracking Code Link
• Built a Real-Time Vehicle Number Plate Recognition and Location Tracking system to help
law enforcement quickly trace suspicious vehicles.
• Combined OpenCV, TensorFlow, and OCR to detect plates and store numbers with camera geolocation
in a MongoDB-based backend for scalable, low-latency retrieval.
• Designed a lightweight Django interface for live monitoring with minimal compute overhead, developed
during my second year.
Work Experience
AI Intern, Infosys Aug 2025 – Oct 2025
• Currently working with the AI team on Generative AI solutions involving Large Language Models
(LLMs) and Natural Language Processing (NLP).
Trainee, IIIT Naya Raipur May 2025 – July 2025
• Led the development of ’SolarPredict,’ a lightweight ML forecasting model, as the capstone project for
the intensive training program, resulting in a submitted IEEE conference paper.
Intern, Krishna Vikash Group of Institutions (KVGI), Odisha Mar 2024 – Apr 2025
• Applied scalable backend design and API integration principles, later leveraged in deploying AI/ML
models into interactive dashboards and real-time monitoring tools.
• Enhanced proficiency in HTML, CSS, JavaScript, and MVC frameworks, strengthening the ability to
integrate AI systems into production-ready applications.
Education
Bachelor of Computer Science and Engineering Oct 2022 - Mar 2026
– Krishna’s Vikash Institute of Technology
Certifications
• Vocational Training Certificate in Python Basics, Data Science, Artificial Intelligence, Machine Learn-
ing, and Deep Learning – IIIT Naya Raipur
• Infosys Principles of Generative AI Certification
• Infosys Artificial Intelligence Primer Certification
• Vocational Training Certificate in Machine Learning with Python – Rays IT and Design World
• Google Cybersecurity Professional Certificate
Skills
Programming Languages Python, JavaScript, HTML, CSS
Frameworks & Libraries TensorFlow, PyTorch, scikit-learn, React, Next.js, Django, OpenCV,
Numpy, Pandas, Matplotlib, Seaborn
Domain Expertise Generative AI, Large Language Models (LLMs), Natural Language Pro-
cessing (NLP), Computer Vision, Data Science, Data Structure, Cloud
Computing
Databases & Tools MongoDB, Git, MySQL, SQL, Postgres, Redis, MS Excel, Power BI
Soft Skills Problem-Solving, Communication, Adaptability, Collaboration, Creativity,
Time Management
Publications
Ash, john SolarPredict: A Lightweight Machine Learning Model Using Weather and Temporal Features.
Paper submitted to an IEEE INDICON conference, December 2025.